A secondary screen architecture to accurately capture viewer interactions in interactive TV environments

### 2014-04-30 src/paper.tex
Added sublime project

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{A secondary screen architecture to improve recommendations in DTV environments by capturing individual user interactions}

@@

\begin{abstract}
%\boldmath
The abstract goes here.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.7 and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill January 11, 2007

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation Results}
%\label{fig_sim}
%\end{figure}

% Note that IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command, the
% \label for the overall figure must come after \caption.
% \hfil must be used as a separator to get equal spacing.
% The subfigure.sty package works much the same way, except \subfigure is
% used instead of \subfloat.
%
%\begin{figure*}[!t]
%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
%\label{fig_second_case}}}
%\caption{Simulation results}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.

% An example of a floating table. Note that, for IEEE style tables, the 
% \caption command should come BEFORE the table. Table text will default to
% \footnotesize as IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
%\begin{table}[!t]
%% increase table row spacing, adjust to taste
%\renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
%\caption{An Example of a Table}
%\label{table_example}
%\centering
%% Some packages, such as MDW tools, offer better commands for making tables
%% than the plain LaTeX2e tabular which is used here.
%\begin{tabular}{|c||c|}
%\hline
%One & Two\\
%\hline
%Three & Four\\
%\hline
%\end{tabular}
%\end{table}

% Note that IEEE does not put floats in the very first column - or typically
% anywhere on the first page for that matter. Also, in-text middle ("here")
% positioning is not used. Most IEEE journals/conferences use top floats
% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
% command of the stfloats package.

\section{Conclusion}
The conclusion goes here \cite{IEEEexample:confwithvolume}.

% conference papers do not normally have an appendix

% use section* for acknowledgement
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\bibliographystyle{IEEEtran}
\bibliography{IEEEexample}

% that's all folks
\end{document}

>>>>

\usepackage{cite}

\begin{document}

\title{A secondary screen architecture to accurately capture viewer interactions in interactive TV environments}

@@

\begin{abstract}
Watching TV is frequently seen as a social activity. Groups of people gather around the television for entertainment or information. One important application for TV viewers is content personalization, which consists in generating personalized content based on viewer interactions. Since the TV set is shared by many people, it is difficult to accurately capture the individual interactions from every viewer using a traditional remote control. As a new trend, the proliferation of personal mobile devices has changed the habits on audiovisual content consumption in interactive TV environments. In many situations people use their personal devices as a secondary screen to perform activities related to television watching. In this paper, we present an architecture for secondary screen devices that facilitates the capture of individual viewer interactions to use in content recommendation. In addition, this architecture can enhance the viewer interaction without interrupting the collective experience while watching TV.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}

Watching TV is essentially a social activity, where family, friends, or people with a common interest share the same space and TV set for entertainment or information~\cite{Masthoff2004}. After many advances in technologies for interactive and digital TV it is possible to develop high level applications to enrich the TV experience. One important application is content personalization, in which content providers deliver personalized content to viewers based on their preferences.

The viewer preferences can be obtained by observing the viewing habits as interactions between the viewers and the TV system. Such interactions can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV e.g., change channel and volume. In explicit interactions viewers contribute by evaluating, commenting or sharing their opinion about a given content. Considering the data of thousands of viewers, the data captured can provide valuable information for content personalization services~\cite{Teixeira2010}.

The traditional remote control as a mechanism of interaction between viewer and TV can present some problems. Since watching TV is a social and collective experience it is difficult to automatically identify the viewer in charge of the remote control. In addition, explicit interactions that require the use of the main screen of the TV set (e.g., evaluate the current content or read comments) ends up interfering in the collective experience. Some researchers tried to address this problem

provide services which deliver personalized content to both individual users and groups of users. Such services depend on user preferences, which can be obtained by observing past viewers interactions with the TV system.

to perform secondary tasks while watching TV

These tasks are frequently related to television watching e.g., evaluating content according to personal tastes, sharing, or even recommending content to other people. This paper presents an architecture that

TV family behaviors towards television.
potential of mobile devices to capture individual user interactions.

opens up new possibilities to accurately capture individual interactions from TV users. by using secondary screen devices.

\bibliographystyle{IEEEtran}
\bibliography{biblio.bib}

\end{document}
